Title Goes Here

### 2021-03-30 analysis/paper/paper.Rmd
Quita intro de PSA
Closes #21
Boludeces de estilo

```{r compute-psi}
psi <- ReadNetCDF(ERA5(), vars = "vo",
                  subset = list(level = c(50, 200),
                                time = c("1979-01-01", "2019-12-01"))) %>%
  normalise_coords() %>%
  .[season(time) == "SON"] %>%
  .[, .(vo = mean(vo)), by = .(lon, lat, lev,time = seasonally(time))] %>%
  .[, solve_poisson(vo, lon, lat), by = .(lev, time)] %>%
  setnames("value", "psi") %>% 
  .[, psi.z := Anomaly(psi), by = .(time, lev, lat)] 
```

@@

We will show that the EOF2 offers an alternative way of representing the PSA which has several advantages over using the second and third principal components. \textcolor{red}{(Esto queda raro porque estas adelantando la conclusión)}

>>>>

```{r compute-psi}
psi <- ReadNetCDF(ERA5(), vars = "vo",
                  subset = list(level = c(50, 200),
                                time = c("1979-01-01", "2019-12-01"))) %>%
  normalise_coords() %>%
  .[season(time) == "SON"] %>%
  .[, .(vo = mean(vo)), by = .(lon, lat, lev, time = seasonally(time))] %>%
  .[, solve_poisson(vo, lon, lat), by = .(lev, time)] %>%
  setnames("value", "psi") %>% 
  .[, psi.z := Anomaly(psi), by = .(time, lev, lat)] 
```

@@
